Research log

### 2023-01-27 docs/preregisteredMethodsAndResults.Rmd
all pre-registered analysis

affiliation:
  - id            : "1"
    institution   : "Birkbeck, University of London"
  - id            : "2"
    institution   : "Johns Hopkins University"s

@@

```{r global_options, include=FALSE}
set.seed(42)
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries, echo=FALSE, warning=FALSE}

@@

<!-- We used `r cite_r("r-references.bib")` for all our analyses. -->

@@

@@

@@

num_clicks_sim = c();
nsim = 10000
boards = rep(NaN,25)

@@

simulated_hits <- data.frame(click_number=1:25,mean_hit=colMeans(boards,na.rm=T))

@@

num_clicks_optimal_sim = c();
nsim = 100;
nboards = all_possible_boards%>%nrow();

for (i in 1:nsim) {
  cur_board = all_possible_boards[sample(1:nboards,1),];
  num_clicks_optimal_sim = c(num_clicks_optimal_sim,simulate_optimal_game(cur_board));
}

@@

@@

@@

@@

@@

@@

E4.df <- read.csv('..\\experiments\\Hangman2\\data\\jatos_results_batch2.csv',na.strings=c(""," ","NA")) %>%
  rbind(read.csv('..\\experiments\\Hangman2\\data\\jatos_results_batch1.csv',na.strings=c(""," ","NA"))) %>%
  rename(subj_id = participant_number) %>%
  mutate(subj_id = factor(subj_id)) %>%
  # the dash is breaking r
  mutate(test_part = ifelse(test_part=='non-pretend','nonpretend',test_part)) %>%
  filter(PROLIFIC_PID != '5ec4a156bc5aac3819ac52f2' & #reported some of the letters not showing up on their screen
        PROLIFIC_PID != '58211fc787f6b90001f13f9' & #reported some of the letters not showing up on their screen
        PROLIFIC_PID != '6149256f6335b06ade3723e0' &  # due a PROLFIIC bug, participated twice
        PROLIFIC_PID != '615ddab1e4f013092538b6c5')# due a PROLFIIC bug, participated twice

@@

E4.click_df <- E4.df %>%
  dplyr::select(subj_id, 
         test_part, 
         category,
         word,
         num_clicks,
         click_log,
         genuine_first,
         trial_type) %>%
  rowwise()%>%
  mutate(num_hits = strsplit(gsub(' ','',word),split='')[[1]]%>%unique()%>%length(),
         genuine_first= genuine_first=='True',
         num_misses = num_clicks-num_hits,
         click_log = gsub("\'","\"", click_log),
         click_log = gsub("None","null", click_log),
         word = factor(word,levels=c(
           'eleven',
           'ninety six',
           'dalai lama',
           'taylor swift',
           'strawberry',
           'lemon',
           'tooth',
           'head',
           'iowa',
           'montana'
         ))) %>%
  filter(test_part=='pretend' | test_part=='nonpretend') %>%
  filter(trial_type=='Hangman')

@@

# E4.click_log <- data.frame(matrix(ncol=11,nrow=0, 
#                                dimnames=list(NULL, 
#                                              c("subj_id",
#                                               "test_part", 
#                                               "word",
#                                               "category",
#                                               "num_clicks",
#                                               "num_misses",
#                                               "letter",
#                                               "hit",
#                                               "t",
#                                               "click_number",
#                                               "genuine_first"))))
# 
# 
# for (row in 1:nrow(E4.click_df)) {
#   
#     subject_click_log <- data.frame(fromJSON(E4.click_df[row, ]$click_log)) %>%
#     mutate(
#       letter = lead(letter,1),
#       t = lead(t,1),
#       hit = lead(hit,1),
#       click_number = 1:n(),
#       subj_id = E4.click_df[row, ]$subj_id,
#       test_part = E4.click_df[row, ]$test_part,
#       word = E4.click_df[row, ]$word,
#       category = E4.click_df[row, ]$category,
#       num_clicks = E4.click_df[row, ]$num_clicks,
#       num_misses = E4.click_df[row, ]$num_misses,
#       genuine_first = E4.click_df[row, ]$genuine_first
#     )%>%
#       filter(click_number<=num_clicks)
#     
#     E4.click_log <- rbind(E4.click_log, subject_click_log);
# }
#     
# 
# E4.click_log <- E4.click_log %>%
#   relocate(subj_id, .before = letter) %>%
#   relocate(genuine_first, .before = letter) %>% 
#   relocate(test_part, .before=letter) %>% 
#   relocate(word, .before=letter) %>% 
#   relocate(category, .before=letter) %>% 
#   relocate(click_number, .before=letter) %>%
#   group_by(subj_id,test_part,word) %>%
#   mutate(RT=t-lag(t,default=0)) %>%
#   group_by(subj_id,word) %>%
#   rowwise()

@@

@@

@@

@@

@@

is_consistent <- function(word_state, asked,  word) {

@@

  word_probabilities <- get_word_prior(category) %>%
    rowwise() %>%
    mutate(likelihood = ifelse(is_consistent(word_state, asked,word),1, 0),
           pword = prior * likelihood) %>%
    ungroup() %>%
    mutate(posterior = pword/sum(pword))%>%
    filter(posterior>0) %>%
    arrange(desc(posterior))

@@

get_posterior <- function(word_state, asked, category) {

@@

get_p_click <- function(posterior, letter) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  return(posterior[which(toupper(letters)==letter)])
}

get_p_click_rank <- function(posterior, letter) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  rank_posterior = rank(-posterior)
  return(rank_posterior[which(toupper(letters)==letter)])
}

# E4.click_log_with_boards <- E4.click_log %>%
#   dplyr::select(subj_id,genuine_first,test_part,word,category,word_state,asked,click_number,letter,RT,hit_bin) %>% 
#   rowwise()%>%
#   mutate(posterior = get_posterior(word_state,asked,category),
#          p_click = get_p_click(posterior,letter),
#          entropy = get_posterior_entropy(posterior),
#          p_click_rank = get_p_click_rank(posterior,letter));

@@

# E4.click_log_with_boards_random <- E4.click_log_with_boards %>%
#   mutate(letter = get_random_letter(asked),
#          p_click = get_p_click(posterior,letter),
#          p_click_rank = get_p_click_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='random');

# E4.click_log_with_boards_most_frequent <- E4.click_log_with_boards %>%
#   mutate(letter = get_most_frequent_letter(asked),
#          p_click = get_p_click(posterior,letter),
#          p_click_rank = get_p_click_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='most_frequent');

# E4.letter_prob_click_log_with_boards <- E4.click_log %>%
#   dplyr::select(subj_id,genuine_first,test_part,word,category,word_state,asked,click_number,letter,RT,hit_bin) %>% 
#   rowwise()%>%
#   mutate(posterior = get_letter_prob_posterior(asked),
#          p_click = get_p_click(posterior,letter),
#          entropy = get_posterior_entropy(posterior),
#          p_click_rank = get_p_click_rank(posterior,letter));

# E4.letter_prob_click_log_with_boards_random <- E4.letter_prob_click_log_with_boards %>%
#   mutate(letter = get_random_letter(asked),
#          p_click = get_p_click(posterior,letter),
#          p_click_rank = get_p_click_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='random');

@@

### Hypothesis 7b (Letter frequency)

@@

@@

### Hypothesis 8(Entropy/RT relationship)

@@

@@

# E4.judge_df <- E4.df %>%
#   filter(test_part=='judge' & trial_type=='html-keyboard-response')%>%
#   dplyr::select(subj_id, 
#          word, 
#          player,
#          correct_response,
#          key_press,
#          correct)%>%
#   rowwise()%>%
#   mutate(used_for_pretend = word_used_for_pretend(subj_id,word),
#          used_for_nonpretend = word_used_for_nonpretend(subj_id,word),
#          common_board = used_for_pretend & used_for_nonpretend,
#          word_type = ifelse(common_board, 'common',
#                              ifelse(used_for_pretend, 'pretend',
#                                     ifelse(used_for_nonpretend,'nonpretend','new')))
# )

@@

E4.pretend_performance <- E4.judge_df %>%
  filter(!(player %in% unidentifiable_ss & pretend==1)) %>%
  group_by(player)%>%
  summarise(ntrials=n(),
            successful=ntrials-sum(correct),
            pretend_rate = successful/ntrials) %>%
  mutate(subj_id=player)

E4.optimality_cost <- E4.click_log_with_boards %>%
  group_by(subj_id,test_part) %>%
  summarise(p_click_rank=mean(p_click_rank)) %>%
  spread(test_part,p_click_rank) %>%
  mutate(optimality_cost=nonpretend-pretend)

E4.performance_df <- merge(E4.judge_performance,
                           E4.pretend_performance) %>%
  merge(E4.optimality_cost);

@@

## Hypothesis 10 (judge-pretend relation)

@@

@@

E4.optimal_letter_choice <- E4.half_game_click_log %>% 
  filter(click_number==1) %>% 
  group_by(word) %>% 
  summarize(posterior = get_posterior(word_state[1],asked[1],category[1]),
            word_state=word_state[1])

@@

## Hypothesis 12 (irrational letter selections)

@@

## Hypothesis 13 (target word effect)

@@

# Discussion

>>>>

affiliation:
  - id            : "1"
    institution   : "Birkbeck, University of London"
  - id            : "2"
    institution   : "Johns Hopkins University"

authornote: |

abstract: |

@@

```{r global_options, include=FALSE}
set.seed(42)
knitr::opts_chunk$set(fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=T, 
                      message=F, sanitize = T, 
                      fig.width = 10, fig.height = 5)
```

```{r, libraries, echo=FALSE, warning=FALSE, cache=F}

@@

@@

```{r battleship-h1-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E2.click_log %>% 
  group_by(subj_id,test_part,grid_number, genuine_first) %>%
  summarise(duration=sum(RT)/1000) %>% 
  group_by(subj_id,test_part,genuine_first) %>% 
  summarise(duration=median(duration)) %>%
  ggplot(aes(x=duration,color=test_part, fill=test_part)) +
  geom_histogram(position='identity',alpha=0.5)  +  
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
    labs(x='game duration (seconds)')+
    theme(legend.position=c(0.10,0.85)) +
    theme_classic()

@@

```{r battleship-h2-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E2.click_log %>% 
  group_by(subj_id,test_part,grid_number, genuine_first) %>%
  summarise(RT=RT[click_number==1]) %>% 
  group_by(subj_id,test_part,genuine_first) %>% 
  summarise(RT=median(RT)) %>%
  filter(RT<20000)%>%
  ggplot(aes(x=RT,color=test_part, fill=test_part)) +
  geom_histogram(position='identity',alpha=0.5)  +  
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
    labs(x='time to first cell selection (ms)')+
    theme(legend.position=c(0.10,0.85)) +
    theme_classic()

@@

num_clicks_sim = c();
nsim = 2500
boards = rep(NaN,25)

@@

@@

# nsim = 2500;
# nboards = all_possible_boards%>%nrow();

# for (i in 1:nsim) {
#   cur_board = all_possible_boards[sample(1:nboards,1),];
#   num_clicks_optimal_sim = c(num_clicks_optimal_sim,simulate_optimal_game(cur_board));
# }
# save(num_clicks_sim, num_clicks_optimal_sim, file='num_clicks_sim.RData')

load('num_clicks_sim.RData')
simulated_hits <- data.frame(click_number=1:25,mean_hit=colMeans(boards,na.rm=T))

@@

```{r battleship-h3-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E2.random_click_df <- data.frame(num_clicks_sim) %>% 
  rename(num_clicks = num_clicks_sim) %>% 
  mutate(test_part='random', 
         subj_id=rep(seq(500),each=5));

num_clicks_optimal_sim_2500 = num_clicks_optimal_sim[1:2500]

E2.optimal_click_df <- data.frame(num_clicks_optimal_sim_2500) %>% 
  rename(num_clicks = num_clicks_optimal_sim_2500) %>% 
  mutate(test_part='optimal', 
         subj_id=rep(seq(500),each=5))

E2.click_df %>%
  dplyr::select(subj_id,test_part, num_clicks) %>%
  mutate(subj_id=as.character(subj_id)) %>%
  rbind(E2.optimal_click_df) %>%
  rbind(E2.random_click_df) %>%
  mutate(test_part = factor(test_part, levels=c(
    'nonpretend','pretend','optimal','random'
  ))) %>%
  group_by(subj_id,test_part) %>%
  summarise(num_clicks=median(num_clicks)) %>%
  ggplot(aes(x=num_clicks,fill=test_part))+
  geom_bar( color="black", alpha=0.6, position = 'identity') +
  scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", 'black')) +
  labs(x='median number of clicks', y='number of players')+
  theme(legend.position=c(0.10,0.85)) +
  theme_classic()

@@

```{r battleship-h4-6-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E2.RT_by_hit_lags_long %>% 
  filter(position<2 & position > -2)%>%
  group_by(test_part,position) %>%
  summarise(median_difference=median(difference),
            sem_difference=bootstrap_error(difference,N_perm)) %>%
  ggplot(aes(x=position,color=test_part,fill=test_part,y=median_difference)) +
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  scale_x_continuous(breaks=-1:1,labels=c('hit on next trial', 'hit on current trial', 'hit on previous trial'))+
  geom_abline(slope=0,intercept=0,linetype=3)+
  geom_path(size=1)+
  geom_ribbon(aes(ymin=median_difference-sem_difference,ymax=median_difference+sem_difference),alpha=0.3,show.legend=F)+
  labs(fill=' ',x='', y='RT effect (ms) of hit on trial t')+
  theme(legend.position=c(0.10,0.85)) +
  theme_classic()

```
### Model based analysis

@@

```{r battleship-h7-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E2.mean_P_click_rank %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="black", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(ship in clicked square) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

@@

```{r battleship-h8-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E2.RT_by_entropy %>%
  ggplot(aes(x=entropy_bin,color=test_part,fill=test_part,y=median_RT)) +
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  geom_path(size=1)+
  geom_ribbon(aes(ymin=median_RT-sem_RT,ymax=median_RT+sem_RT),alpha=0.3,show.legend=F)+
  labs(fill=' ',x='Entropy of posterior', y='median RT (ms)')+
  theme_classic()

@@

```{r battleship-h10-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

# E2.performance_df %>%
#   group_by(judge_rate) %>%
#   summarise(mean_pretend_rate = mean(pretend_rate),
#             se_pretend_rate=se(pretend_rate)) %>%
#   ggplot(aes(x=judge_rate, y=mean_pretend_rate, 
#          ymin=mean_pretend_rate-se_pretend_rate, 
#          ymax=mean_pretend_rate+se_pretend_rate)) +
#   geom_point(size=3) +
#   geom_errorbar()

E2.performance_df %>%
  ggplot(aes(x=pretend_rate, y=judge_rate)) +
  geom_point() +
  labs(x= 'successful pretense rate', y='judge accuracy') +
  theme_classic()

@@

E4.df <- read.csv('..\\experiments\\Hangman2\\data\\jatos_results_batch2.csv',na.strings=c(""," ","NA")) %>%
  rbind(read.csv('..\\experiments\\Hangman2\\data\\jatos_results_batch1.csv',na.strings=c(""," ","NA"))) %>%
  mutate(subj_id = paste(as.character(participant_number),substr(PROLIFIC_PID,1,5),sep='')) %>%
  mutate(subj_id = factor(subj_id)) %>%
  # the dash is breaking r
  mutate(test_part = ifelse(test_part=='non-pretend','nonpretend',test_part)) %>%
  filter(PROLIFIC_PID != '5ec4a156bc5aac3819ac52f2' & #reported some of the letters not showing up on their screen
        PROLIFIC_PID != '58211fc787f6b90001f13f9' & #reported some of the letters not showing up on their screen
        PROLIFIC_PID != '6149256f6335b06ade3723e0' &  # due a PROLFIIC bug, participated twice
        PROLIFIC_PID != '615ddab1e4f013092538b6c5')# due a PROLFIIC bug, participated twice

@@

E4.click_df <- E4.df %>%
  dplyr::select(subj_id, 
         PROLIFIC_PID,
         test_part, 
         category,
         word,
         num_clicks,
         click_log,
         genuine_first,
         trial_type) %>%
  rowwise()%>%
  mutate(num_hits = strsplit(gsub(' ','',word),split='')[[1]]%>%unique()%>%length(),
         genuine_first= genuine_first=='True',
         num_misses = num_clicks-num_hits,
         click_log = gsub("\'","\"", click_log),
         click_log = gsub("None","null", click_log),
         word = factor(word,levels=c(
           'eleven',
           'ninety six',
           'dalai lama',
           'taylor swift',
           'strawberry',
           'lemon',
           'tooth',
           'head',
           'iowa',
           'montana'
         ))) %>%
  filter(test_part=='pretend' | test_part=='nonpretend') %>%
  filter(trial_type=='Hangman')

@@

# E4.click_log <- data.frame(matrix(ncol=11,nrow=0,
#                                dimnames=list(NULL,
#                                              c("subj_id",
#                                               "test_part",
#                                               "word",
#                                               "category",
#                                               "num_clicks",
#                                               "num_misses",
#                                               "letter",
#                                               "hit",
#                                               "t",
#                                               "click_number",
#                                               "genuine_first"))))

# for (row in 1:nrow(E4.click_df)) {
# 
#     subject_click_log <- data.frame(fromJSON(E4.click_df[row, ]$click_log)) %>%
#     mutate(
#       letter = lead(letter,1),
#       t = lead(t,1),
#       hit = lead(hit,1),
#       click_number = 1:n(),
#       subj_id = E4.click_df[row, ]$subj_id,
#       test_part = E4.click_df[row, ]$test_part,
#       word = E4.click_df[row, ]$word,
#       category = E4.click_df[row, ]$category,
#       num_clicks = E4.click_df[row, ]$num_clicks,
#       num_misses = E4.click_df[row, ]$num_misses,
#       genuine_first = E4.click_df[row, ]$genuine_first
#     )%>%
#       filter(click_number<=num_clicks)
# 
#     E4.click_log <- rbind(E4.click_log, subject_click_log);
# }

# E4.click_log <- E4.click_log %>%
#   relocate(subj_id, .before = letter) %>%
#   relocate(genuine_first, .before = letter) %>%
#   relocate(test_part, .before=letter) %>%
#   relocate(word, .before=letter) %>%
#   relocate(category, .before=letter) %>%
#   relocate(click_number, .before=letter) %>%
#   group_by(subj_id,test_part,word) %>%
#   mutate(RT=t-lag(t,default=0)) %>%
#   group_by(subj_id,word) %>%
#   rowwise()

# save(E4.click_log, file='E4.click_log.RData')

@@

```{r hangman-duration-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E4.click_log %>% 
  group_by(subj_id,test_part,word, genuine_first) %>%
  summarise(duration=sum(RT)/1000) %>% 
  group_by(subj_id,test_part,genuine_first) %>% 
  summarise(duration=median(duration)) %>%
  ggplot(aes(x=duration,color=test_part, fill=test_part)) +
  geom_histogram(position='identity',alpha=0.5)  +  
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
    labs(x='game duration (seconds)')+
    theme(legend.position=c(0.10,0.85)) +
    theme_classic()

@@

```{r hangman-h2-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E4.time_per_click_number %>% 
  filter(click_number==1 & subj_id != '5975df4') %>%
  mutate(RT=RT/1000)%>%
  filter(RT<40) %>%
  ggplot(aes(x=RT,color=test_part, fill=test_part)) +
  geom_histogram(position='identity',alpha=0.5)  +  
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
    labs(x='time to first cell selection (seconds)')+
    theme(legend.position=c(0.10,0.85)) +
    theme_classic()

@@

```{r hangman-h3-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E4.click_df %>%
  group_by(subj_id,test_part) %>%
  summarise(num_misses=median(num_misses)) %>%
  mutate(test_part = factor(test_part, levels=c(
    'nonpretend','pretend','optimal','random'
  ))) %>%
  group_by(subj_id,test_part) %>%
  summarise(num_clicks=median(num_misses)) %>%
  ggplot(aes(x=num_clicks,fill=test_part))+
  geom_bar( color="black", alpha=0.6, position = 'identity') +
  scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725", 'black')) +
  labs(x='median number of misses', y='number of players')+
  theme(legend.position=c(0.10,0.85)) +
  theme_classic()

@@

```{r hangman-h4-6-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E4.RT_by_hit_lags_long %>% 
  filter(position<2 & position > -2)%>%
  group_by(test_part,position) %>%
  summarise(median_difference=median(difference, na.rm=T),
            sem_difference=bootstrap_error(difference,N_perm)) %>%
  ggplot(aes(x=position,color=test_part,fill=test_part,y=median_difference)) +
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  scale_x_continuous(breaks=-1:1,labels=c('hit on next trial', 'hit on current trial', 'hit on previous trial'))+
  geom_abline(slope=0,intercept=0,linetype=3)+
  geom_path(size=1)+
  geom_ribbon(aes(ymin=median_difference-sem_difference,ymax=median_difference+sem_difference),alpha=0.3,show.legend=F)+
  labs(fill=' ',x='', y='RT effect (ms) of hit on trial t')+
  theme(legend.position=c(0.10,0.85)) +
  theme_classic()

@@

word_is_consistent <- function(word_state, asked,  word) {

@@

  word_probabilities <- get_word_prior(category) %>%
    rowwise() %>%
    mutate(likelihood = ifelse(word_is_consistent(word_state, asked,word),1, 0),
           pword = prior * likelihood) %>%
    ungroup() %>%
    mutate(posterior = pword/sum(pword))%>%
    filter(posterior>0) %>%
    arrange(desc(posterior))

@@

get_letter_posterior <- function(word_state, asked, category) {

@@

get_p_letter <- function(posterior, letter) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  return(posterior[which(toupper(letters)==letter)])
}

get_p_letter_rank <- function(posterior, letter) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  rank_posterior = rank(-posterior)
  return(rank_posterior[which(toupper(letters)==letter)])
}

get_letter_posterior_entropy <- function(posterior) {
  posterior <- scan(text= posterior, what = numeric(), sep="," , quiet = TRUE);
  posterior[which(posterior==0)]=NA; #to avoid infinity*0
  entropy <- -sum(unlist(posterior)*(unlist(log(posterior))),na.rm=TRUE);
  return(entropy);
}

# E4.click_log_with_boards <- E4.click_log %>%
#   dplyr::select(subj_id,genuine_first,test_part,word,category,word_state,asked,click_number,letter,RT,hit_bin) %>%
#   rowwise()%>%
#   mutate(posterior = get_letter_posterior(word_state,asked,category),
#          p_click = get_p_letter(posterior,letter),
#          entropy = get_letter_posterior_entropy(posterior),
#          p_click_rank = get_p_letter_rank(posterior,letter));

@@

# E4.click_log_with_boards_random <- E4.click_log_with_boards %>%
#   mutate(letter = get_random_letter(asked),
#          p_click = get_p_letter(posterior,letter),
#          p_click_rank = get_p_letter_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='random');

# E4.click_log_with_boards_most_frequent <- E4.click_log_with_boards %>%
#   mutate(letter = get_most_frequent_letter(asked),
#          p_click = get_p_letter(posterior,letter),
#          p_click_rank = get_p_letter_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='most_frequent');

# E4.letter_prob_click_log_with_boards <- E4.click_log %>%
#   dplyr::select(subj_id,genuine_first,test_part,word,category,word_state,asked,click_number,letter,RT,hit_bin) %>%
#   rowwise()%>%
#   mutate(posterior = get_letter_prob_posterior(asked),
#          p_click = get_p_letter(posterior,letter),
#          entropy = get_letter_posterior_entropy(posterior),
#          p_click_rank = get_p_letter_rank(posterior,letter));

# E4.letter_prob_click_log_with_boards_random <- E4.letter_prob_click_log_with_boards %>%
#   mutate(letter = get_random_letter(asked),
#          p_click = get_p_letter(posterior,letter),
#          p_click_rank = get_p_letter_rank(posterior,letter),
#          hit_bin = tolower(letter) %in% strsplit(tolower(word),'')[[1]],
#          test_part='random');

# save(E4.click_log_with_boards,
#      E4.click_log_with_boards_random,
#      E4.click_log_with_boards_most_frequent,
#      E4.letter_prob_click_log_with_boards,
#      E4.letter_prob_click_log_with_boards_random,
#      file='E4.click_log_with_boards.RData')

@@

```{r hangman-h7-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E4.mean_P_click_rank %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="black", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(ship in clicked square) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

```
### Hypothesis 7b (Letter frequency)

@@

```{r hangman-h7b-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E4.mean_letter_prob_P_click_rank %>%
    filter(test_part != 'optimal') %>%
    mutate(genuine_first = ifelse(genuine_first, 'non-pretend then pretend', 'pretend then non-pretend'))%>%
    ggplot(aes(x=p_click_rank,fill=test_part))+
    geom_histogram( color="black", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
    labs(x='p(ship in clicked square) - rank', y='number of players')+
    theme(legend.position=c(0.10,0.85)) +
    # facet_wrap(~genuine_first, nrow=2)+
    # scale_x_reverse() +
    theme_classic();

@@

### Hypothesis 8 (Entropy/RT relationship)

@@

```{r hangman-h8-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E4.click_log_with_boards %>%
  filter(click_number>1) %>%
  mutate(entropy_bin=round(entropy*3)/3) %>%
  group_by(test_part,subj_id,entropy_bin) %>% 
  summarise(RT=median(RT)) %>%
  group_by(test_part,entropy_bin) %>%
  summarise(median_RT=median(RT),
            sem_RT=bootstrap_error(RT,N_perm)) %>%
  ggplot(aes(x=entropy_bin,color=test_part,fill=test_part,y=median_RT)) +
  scale_fill_manual(values=c("#69b3a2", "#404080")) +
  scale_color_manual(values=c("#69b3a2", "#404080")) +
  geom_path(size=1)+
  geom_ribbon(aes(ymin=median_RT-sem_RT,ymax=median_RT+sem_RT),alpha=0.3,show.legend=F)+
  labs(fill=' ',x='Entropy of posterior', y='median RT (ms)')+
  theme_classic()

@@

# E4.judge_df <- E4.df %>%
#   filter(test_part=='judge' & trial_type=='html-keyboard-response')%>%
#   dplyr::select(subj_id,
#          word,
#          player,
#          correct_response,
#          key_press,
#          correct)%>%
#   rowwise()%>%
#   mutate(used_for_pretend = word_used_for_pretend(subj_id,word),
#          used_for_nonpretend = word_used_for_nonpretend(subj_id,word),
#          subj_id = as.numeric(substr(subj_id,1,3)),
#          common_board = used_for_pretend & used_for_nonpretend,
#          word_type = ifelse(common_board, 'common',
#                              ifelse(used_for_pretend, 'pretend',
#                                     ifelse(used_for_nonpretend,'nonpretend','new')))
# )

@@

E4.pretend_performance <- E4.judge_df %>%
  mutate(pretend = correct_response=='P')%>%
  filter(!(player %in% unidentifiable_ss) & pretend) %>%
  group_by(player)%>%
  summarise(ntrials=n(),
            successful=ntrials-sum(correct),
            pretend_rate = successful/ntrials) %>%
  mutate(subj_id=player)

E4.optimality_cost <- E4.click_log_with_boards %>%
  mutate(subj_id = as.numeric(substr(subj_id,1,3))) %>%
  filter(!(subj_id %in% unidentifiable_ss)) %>%
  group_by(subj_id,test_part) %>%
  summarise(p_click_rank=mean(p_click_rank)) %>%
  spread(test_part,p_click_rank) %>%
  mutate(optimality_cost=nonpretend-pretend)

E4.performance_df <- merge(E4.judge_performance,
                           E4.pretend_performance %>%
                             dplyr::select(subj_id,pretend_rate)) %>%
  merge(E4.optimality_cost, by='subj_id');

@@

@@

```{r hangman-h10-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

# E4.performance_df %>%
#   group_by(judge_rate) %>%
#   summarise(mean_pretend_rate = mean(pretend_rate),
#             se_pretend_rate=se(pretend_rate)) %>%
#   ggplot(aes(x=judge_rate, y=mean_pretend_rate,
#          ymin=mean_pretend_rate-se_pretend_rate,
#          ymax=mean_pretend_rate+se_pretend_rate)) +
#   geom_point(size=3) +
#   geom_errorbar()

E4.performance_df %>%
  ggplot(aes(x=pretend_rate, y=judge_rate)) +
  geom_point() +
  labs(x= 'successful pretense rate', y='judge accuracy') +
  theme_classic()

@@

E4.optimal_letter_choice <- E4.half_game_click_log %>% 
  filter(click_number==1) %>% 
  group_by(word) %>% 
  summarize(posterior = get_letter_posterior(word_state[1],asked[1],category[1]),
            word_state=word_state[1])

@@

### Hypothesis 12 (irrational letter selections)

@@

```{r hangman-h12-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

N_perm <- 1000;
bootstrap_error_binomial <- function(x, N_perm) {
  N <- length(x)
  means = c();
  for (i in 1:N_perm) {
    means = c(means,sample(x,replace=TRUE,size=N)%>%mean())
  };
  return(sd(means))
}

E4.first_click_half_games %>%
  group_by(test_part) %>%
  summarise(se = bootstrap_error_binomial(makes_sense,N_perm),
            makes_sense=mean(makes_sense)) %>%
  mutate(test_part=ifelse(test_part=='pretend_half_game','pretend','non-pretend')) %>%
  ggplot(aes(x=test_part,fill=test_part,y=makes_sense))+
  geom_bar(position=position_dodge(),
           stat='identity', color='black')+
  geom_errorbar(aes(ymax = makes_sense+se, ymin=makes_sense-se))+
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
  theme_classic()+
  labs(y='proportion of clicks that make sense')

### Hypothesis 13 (target word effect)

@@

```{r hangman-h13-plot, echo-FALSE, cache=TRUE, fig.width=10,fig.height=5}

E4.first_click_half_games %>%
  filter(makes_sense)%>%
  mutate(word_class = ifelse(word %in% c('banana','hand'),'BANANA or HAND','PAPAYA or HAIR'))%>%
  group_by(test_part,word_class) %>%
  summarise(se = bootstrap_error_binomial(bananahand,N_perm),
            bananahand= mean(bananahand)) %>%
  mutate(test_part=ifelse(test_part=='pretend_half_game','pretend','non-pretend')) %>%
  ggplot(aes(x=test_part,fill=test_part,y=bananahand))+
  geom_bar(position=position_dodge(),
           stat='identity', color='black')+
  geom_errorbar(aes(ymax = bananahand+se, ymin=bananahand-se))+
    scale_fill_manual(values=c("#69b3a2", "#404080", "#FDE725")) +
  theme_classic()+
  facet_grid(col=vars(word_class))+
  labs(y='(consistent with BANANA/HAND)/(cons. with something)')
